Differential invariant signatures for planar Lie group transformations of images

### 2019-12-18 paper/newpaper.tex
words

\section{Introduction}
\todo[inline]{Examples to be numbered like theorems}
\todo[inline]{This is a start. To be completed later.}

@@

local invariants -> occlusions OK
derivatives -> noise is not

signatures, dimensions, orders

@@

@@

@@

\todo[inline]{E(2) is confusing. Robert did it by contraction, and got nice invariants. For the moving frame, the issue is that you have to consider one of the branches, since there is a reflection ambiguity. This is hacked in the PSL(3,R) case. Even then, it isn't clear that you can get the nice ones. The same issue stands for trying to extend SE(2) to E(2).

Question: is there an extension of transvectants (change of operator) that lets you get to it that way?

However... we should do Sim(2) by adding a scaling to E(2), so we need it :(
}

@@

\todo[inline]{Richard to find the moving frame version!}

@@

\section{Algorithms}
 This will go in paper 2, but let's start in here.

\todo[inline]{Pseudocode for the matlab experimental code}
\todo[inline]{Something about computing transvectants?}

\section{Experiments}

\todo[inline]{Signature examples}
\todo[inline]{Noise}
\todo[inline]{Spot the group}
\todo[inline]{Example on bits of images}

\section{Discussion}

>>>>

\section{Introduction}
\todo[inline]{
Richard:

Stephen:

}

\todo[inline]{Examples to be numbered like theorems}
\todo[inline]{This is a start. To be completed later.}

@@

\todo[inline]{Use T(2) as an example}

local invariants: occlusions OK
derivatives: noise is not

signatures, dimensions, orders
Bad set, completeness

@@

\section{The Invariant Tensor Theorem}

The new contraction mapping computation.

E(2), Sim(2)

Since this will be the first example, put the details of the image here. And remove one of the repeats below.

3D and 4D signatures.

@@

\todo[inline]{This needs a friendly introduction, or at least a pointer to the notebooks}

@@

\todo[inline]{ Two things to note: (1) SE(2) has similar invars, (2) there is an issue in E(2) with the moving frame: reflection ambiguity. That's why we did it by contraction.
}

@@

\todo[inline]{Put the moving frame version here}

@@

Some calculation detail

\todo[inline]{Signature examples}
\todo[inline]{Alien: Smoothing, noise}
\todo[inline]{Spot the group?}

\section{Conclusions}

\todo[inline]{Number of derivatives}
\item[inline]{Noise; integral invariants, Fourier}
\todo[inline]{Is there a general theory - syzygy??}
